%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Full Stack Developer} % Job title
    {Oak City Labs} % Organization
    {Apex, NC} % Location
    {Nov 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Work directly with clients to build and maintain custom full stack web applications deployed on AWS resources.}
        \item {Mentor and manage a junior developer, reviewing pull requests and ensuring thorough testing and best practices.}
        \item {Updated stack from services run on VMs to containers deployed in a multi-AZ Docker Swarm cluster.}
        \item {Extensive use of Python, Flask, FastAPI, SQLAlchemy, Typescript/Javascript, Vue.js, React, PostgreSQL, AWS (EC2, EBS, RDS, ELB, S3, ECS, ECR, AWS Batch, IAM, VPC, Lambda, and more), Docker containers, Docker Swarm, Linux, Ansible, NGINX, Traefik.}
        \item {Set up CI/CD pipelines with Ansible, Github Actions, and TeamCity.}
        \item {Prioritize testing with pytest and Jest.}
        \item {Designed and built an application for Botanacor (acquired in 2022) for dynamically generating and customizing cannabis quality control lab result PDF's. Utilized ReportLab, FastAPI, Vue.js, Celery, Docker Swarm.}
        \item {Designed and built a HIPAA compliant application to collect and visualize a state's success outcomes within a federally funded program. Included designing a secure application architecture in AWS, maintaining audit trails around sensitive database records, and dynamic generation of Excel files with custom data validation.}
        \item {Designed and built \href{https://fdi2.com}{fdi2.com} for the Florida Dysphagia Institute, a platform for healthcare providers to register for courses and recieve MDTP certification. Integrated with Eventzilla for event ticketing and Thinkific for administering certification exams. Utilized Stripe, FastAPI, Vue.js, Wagtail CMS, Docker Swarm.}
        \item {Designed and built the Callisto backend, a FastAPI server and Celery distributed task queue for provisioning AWS EC2 servers, allowing the Callisto Mac App to run Jupyter notebooks in the cloud. Functions include creating/starting/stopping EC2 instances, connecting via SSH to bootstrap them, monitoring them for availability, and tracking usage throughout the month to bill users via Stripe.}
        \item {Designed and built the Callisto Jupyter D1 library, a FastAPI server using the jupyter\_client library to control Jupyter kernels and maintain Jupyter notebook state in a central fashion, sending updates to connected clients using websockets.}
        \item {Designed and built an API for VitalFlo to collect spirometry data and other metrics from their iOS app and aggregate air quality data from IoT devices and third party API's. Utilized Flask, SQLAlchemy, Pandas, Flask Admin, PostgreSQL, Ansible.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Android Developer} % Job title
    {Oak City Labs} % Organization
    {Apex, NC} % Location
    {Nov 2016 - Jun 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked directly with clients to build custom native Android apps.}
        \item {Extensive use of Kotlin and Java, data persistence with Realm and Room, dependency injection with Dagger and Koin, ReactiveX style asynchronous programming with RxJava/RxAndroid, HTTP API usage with Retrofit, image loading with Glide and Fresco, background processing with WorkManager, maps and location with Google Maps and Mapbox, and testing with JUnit and Mockito.}
        \item {Set up CI/CD pipelines publishing to the Google Play store with fastlane.}
        \item {Designed and built the CurEat Android app for finding, curating, and sharing local restaurants.}
        \item {Designed and built an Android app for a Fortune 500 agricultural company that displays custom satellite imagery tiles with the Mapbox SDK. Includes support for background downloading and caching of tiles for later offline use.}
        \item {Designed and built an Android app for a medical school that provides resources and an interactive public forum to improve mental health and wellness of faculty, staff, and students.}
        \item {Built a custom Android library for communicating with a hardware device via MQTT.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Developer} % Job title
    {WedPics} % Organization
    {Raleigh, NC} % Location
    {Feb 2016 - Sep 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and updated the WedPics Android app.}
        \item {Implemented in-app purchases with Google Play, updated UI with new designs, debugged features, and helped implement new image editing features with OpenGL.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
